Make any stupid plot you want

### 2021-01-15 draft/sections/implementation.tex
feedback + local
moving files, start of implementation, fightes with minted

\documentclass[../main.tex]{subfiles}
\begin{document}
\section{Matplottoy}
\begin{figure}
\includegraphics[width=\linewidth]{figures/sections/math/path_of_q.png}
\end{figure}
%%% objects: Data, V, H
%%% functions: \nu, q

We build on top of the existing Matplotlib architecture \cite{hunterMatplotlib2DGraphics2007} so that we can initially focus on the data to graphic transformations and rely on Matplotlib for the other graphical elements of the visualization and the rendering. For a primitive graph such as a bar, scatter, line, our path is: 
\begin{minted}{python}

E = Section()
V = {'parameter': ('field': transformer)}

fig, ax = plt.subplots()
artist = primative_Q(E, V)
ax.add_artist(artist)
\end{minted}

\subsection{Data: $\mathcal{E}$}
We propose a semantic markup of the fiber and connectivity that we will later use to check the constraints of the $\nu$ and $Q$. 
\begin{minted}{python}
class FiberBundle:
    def __init__(self, K, F):
            """
            K: {'tables':[]}
            F: {'field name': (type, monoid action)}
            """

    def is_section(self, section):
        """checks if a section is from a given fiber bundle:
        are values in F, are keys in K"""
\end{minted}
We add a monoid field to the schema like structure of the fiber since the monoid actions are the constraints on the $\nu$ and $Q$. We implement $K$ using the triangulization scheme described in section~\ref{sec:triangulization}. This means we expect data to be provided as tables where the name encodes the connectivity:

\begin{description}
    \item[vertex] - disconnected points
    \item[edge] - 1D continuity along the edge
    \item[face] - 2D continuity along the face
\end{description}
Nested continuity is encoded in the fiber. For example, one way to encode a movie is a 1D timeseries of \mathrm{Frame} objects, where each \mathrm{Frame} is a $n\x m$ continuous array.

\subsubsection{Sections}
As described in section~\ref{sec:section_data}, the data values are encode as the section of the fiber bundle. We implement this as as a wrapper class around a data container object of the form:
\begin{minted}
class Section:
    FB = FiberBundle(K, F)

    def __init__(self, *args):
        pass
    def view(self, simplex="vertex"):
        """"converts data into atomic column order for get method
        # maybe also pass in the columns?
        """
        return {fieldname: data}
\end{minted}

The view function is the closest analog to $\tau$, as it returns a a data container type object. We specify field based top level indexing so that we can pair the fields with transformer $\nu$ objects.

\subsection{Encoding: $\mathcal{V}$}
We implement $\nu$ as encoder objects with an optional `__init__` method that can be used to specify the range of target visual variables.

\begin{minted}{python}
class Encoder:
    def __init__(self, args):
        pass
    def validate(self, monoid):
        pass
    def convert(self, value):
        return converted_value
\end{minted}

The \mathrm{validate} method specifies the monoids for which this a valid $\nu$ and checks against the specification in the fiber. The \mathrm{convert} method converts a value from data space to an internalized normal form as described in table~\ref{tab:mpl_visual_variable_fiber}.

\subsection{Graphic: $\mathcal{H}$}

\subsection{Case Study: Iris(Penguins)}

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}

\section{Matplottoy}

We build on the existing Matplotlib architecture \cite{hunterMatplotlib2DGraphics2007} so that we can initially focus on the data to graphic transformations and rely on Matplotlib for the other graphical elements of the visualization and the rendering. We first introduce an implementation of scatter, line, and bar charts because they map to the fundemental marks of point, line, and area. We then introduce aggregated bar charts to show how to build more complex graphics.

\subsection{Scatter}
 A scatter plot \cite{friendlyBriefHistoryData2006a,tukeyExploratoryDataAnalysis1977} is a chart type for plotting discrete values against each other. Minimally a scatter plot requires and x or y position, but the other variables in our dataset can be mapped to visual aspects of the scatter graphical mark. 
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/code/scatter_0.png}
    \label{fig:scatter}
\end{figure}

For the scatter plot in figure~\ref{fig:scatter}, we define $Q$ as 
 \begin{equation}
    Q(\mu_{xpos}, \mu_{ypos}, \mu_{facecolor}, \mu_{s})
 \end{equation}

which we implement building on the \texttt{matplotlib.collections} API:

\begin{minted}{python}
    class Point(mcollections.Collection):
        # this is the visual fiber 
        required = {'x', 'y'}
        optional = {'facecolors', 's'} 
        def __init__(self, data, transforms, *args, **kwargs):
            """
            Parameters
            ----------
            data: sections of the fiber bundle
            transforms
            """
            super().__init__(*args, **kwargs)

            # check that the data you're trying to transform 
            # has a way to provide vertex data  
            assert 'vertex' in data.FB.K['tables']
            # check that you've given the required parameters
            utils.check_constraints(Point, transforms.keys())
            utils.validate_transforms(data.FB.F, transforms)

            self.data = data
            self.transforms = transforms

        def draw(self, renderer, *args, **kwargs):
            view = self.data.view('vertex') #resolve to size

            # call tau step
            visual = utils.convert_transforms(view, self.transforms)

            # assembles taus to generate idiom
            # dictionary here in place of visual(parameter) function

            visual['s'] = itertools.repeat(visual.get('s', 0.05))
            visual['facecolors'] = visual.get('facecolors', "C0")
            #switch out to a marker 
            self._paths = [mpath.Path.circle(center=(x,y), radius=s)  
                            for (x, y, s) 
                            in zip(visual['x'],visual['y'], visual['s'])]

            self.set_facecolors(visual['facecolors'])
            super().draw(renderer, *args, **kwargs)
    \end{minted}
